Secure Composition of Robust and Optimising Compilers

### 2023-07-12 popl/main.tex
proofs

\begin{theorem}[Compiler $\cca\circ\ccb$ is secure with respect to \gls*{ms}]\label{thm:ccab:rtp:ms}
  $\rtp{\cca\circ\ccb}{\mssafe}$ % \Coqed
\end{theorem}

@@

\begin{theorem}[Compiler $\ccmsscct$ is secure with respect to \gls*{scct}]\label{thm:ccall:rtp:msscct}
  $\rtp{\cc{\Ltms}{\Lscct}}{\mssafe\cap\scctsafe}$ \Coqed
\end{theorem}
\begin{proof}
	From \Thmref{thm:ccscct:rtp:scct}, we have that any LTMS program $\src{p}$ gets compiled into a L program $\trg{p}$ that is also TMS.
	Then, from \Thmref{thm:cccfccdce:rtp:ms} we have that $\trg{p}$ gets compilet to a program ?? that is also SMS, assuming it was SMS to begin with.
	Since TMS + SMS = MS, ?? is MS.
	?? gets optimised by the optimisation passes and its optimisation is ???, which is still MS.
	Finally, \Thmref{thm:ccab:rtp:ms} ensures that ??? gets compiled into ????, which is CCT assuming that the original program was CCT to begin with.
	\MPin{please fill in the macros here}
  % \MKin{%
  %   \textbackslash Thmref or \textbackslash Cref?
  % }
% Unfold the definition of $\rtp{\cc{\Ltms}{\Lscct}}{\mssafe\cap\scctsafe}$.
% So, let $\pi\in\mssafe\cap\scctsafe$, $\src{\progvar}$ such that $\rsat{\src{\progvar}}{\pi}$ and let $\obj{\contextvar},\obj{\runtimetermvar}$ with $\progstepto{\prog[\obj]{\obj{\contextvar}}{\left(\cc{\Ltms}{\Lscct}(\src{\progvar})\right)}}{\obj{\runtimetermvar}}{\obj{\trace}}$.
% What is left to show is $\scctfilterLscct[\emptyset]{\obj{\trace}}\in\pi$.
% Let $\irl{\progvar}=\cc{\Ltms}{\Ltrg}\circ\cc{\Ltrg}{\Lms}\circ\cc[\gls*{cf}]{\Lms}{\Lms}\circ\cc[\gls*{dce}]{\Lms}{\Lms}(\src{\progvar})$ such that $\cc{\Lms}{\Lscct}(\irl{\progvar})=\cc{\Ltms}{\Lscct}(\src{\progvar})$.
% Note that $\pi\in\scctsafe$, so apply \Thmref{thm:ccscct:rtp:scct}
\end{proof}

>>>>

\begin{theorem}[Compiler $\cca\circ\ccb$ is secure with respect to \gls*{ms}]\label{thm:ccab:rtp:ms}
  $\rtp{\cca\circ\ccb}{\mssafe}$ % \Coqed
\end{theorem}
\begin{proof}
  From \Thmref{thm:cca:rtp:tms} it follows that for any $\Ltms$ program $\src{\progvar}$, it compiles to an $\Ltrg$ program $\trg{\progvar}$ that robustly satisfies \gls*{tms}.
  Note that $\src{\progvar}$ robustly satisfies \gls*{tms} by the properties of the typesystem of $\Ltms$.
  Then, \Thmref{thm:ccb:rtp:sms} demonstrates that, assuming $\trg{\progvar}$ robustly satisfies \gls*{sms}, the program $\trg{\progvar}$ compiles to an $\Lms$ program $\irl{p}$ that also robustly satisfies \gls*{sms}.
  From \Thmref{thm:ccab:rtp:ms} it follows that $\src{p}$ compiles to $\irl{p}$ that robustly satisfies \gls*{ms}, since \gls*{ms} is the intersection of \gls*{tms} and \gls*{sms}.
\end{proof}

@@

\begin{theorem}[Compiler $\ccmsscct$ is secure with respect to \gls*{scct}]\label{thm:ccall:rtp:msscct}
  $\rtp{\cc{\Ltms}{\Lscct}}{\mssafe\cap\scctsafe}$ \Coqed
\end{theorem}
\begin{proof}
	From \Thmref{thm:ccab:rtp:ms}, we have that any $\Ltms$ program $\src{\progvar}$ compiles into a $\Lms$ program $\irl{\progvar}$ that robustly satisfies \gls*{ms}.
	Then, from \Thmref{thm:cccfccdce:rtp:ms} we have that $\irl{\progvar}$ gets optimised to a program $\irl{\progvar[']}$ that is also \gls*{ms}, where the order of optimisations does not matter for $\irl{\progvar[']}$ to be \gls*{ms}.
  Assuming $\irl{\progvar[']}$ robustly satisfies \gls*{scct}, by \Thmref{thm:ccscct:rtp:scct} it compiles to an $\Lscct$ program $\obj{\progvar}$ that robustly satisfies \gls*{scct} as well.
  Finally, from \Thmref{thm:rtp} it follows that, given $\src{\progvar}$ robustly satisfies \gls*{scct} and \gls*{ms}, $\obj{\progvar}$ also robustly satisfies \gls*{scct} and \gls*{ms}.
\end{proof}
